### 2012-03-28 contents.tex
Minor changes after conference review.

However, mining bug repositories has its own risks. Previous research has identified problems of missing data (e.g., rationale, traceability links between reported bug fixes and source code changes) and inaccurate data (e.g., misclassification of bugs) \cite{Aranda2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

	\begin{itemize}
		\item \textbf{How} is the verification performed: are there performed ad hoc tests, automated tests, code inspection?
		\item \textbf{Who} performs the verification: is there a QA (quality assurance) team? 
		\item \textbf{When} is the verification performed: is it performed just after the fix, or is there a verification phase?
		% \item How is the distribution of verification across developers?
		% \item Is there a dedicated team for QA?
	\end{itemize}

@@

	In order to perform the desired analyses, we needed access to the data recorded by Bugzilla for a specific project, including status changes and comments. We have found such data for two projects---Eclipse and NetBeans---from the domain of integrated development environments. The data were made available as part of the Mining Software Repositories 2011 Challenge\footnote{\url{http://www.msrconf.org/msr-challenge.html}} in the form of MySQL database dumps. The files contain all data from the respective databases, except for developer profiles, omitted for privacy reasons.

@@

	Also, we have obtained the release dates for multiple versions of Eclipse and NetBeans. The information was obtained in the respective websites. In cases in which older information was not available, archived versions of the web pages were accessed via the website \url{www.archive.org}.

@@

	In Eclipse/Platform, the developer who fixes a bug often someone else to verify the fix, by asking ``please verify, [developer name]''. If the bug is reopened, then the fixer and the verifier exchange roles. This behavior illustrates a structured bug fixing/verification process.

@@

The first author is supported by FAPESB under grant BOL0119/2010.

>>>>

However, mining bug repositories has its own risks. Previous research has identified problems of missing data (e.g., rationale, traceability links between reported bug fixes and source code changes), inaccurate data (e.g., misclassification of bugs) \cite{Aranda2009}, and biased data \cite{Bird2009}. %,Bird2009,Nguyen2010,Ayari2007}.

@@

	\begin{itemize}
		\item \textbf{When} is the verification performed: is it performed just after the fix, or is there a verification phase?
		\item \textbf{Who} performs the verification: is there a QA (quality assurance) team? 		
		\item \textbf{How} is the verification performed: are there performed ad hoc tests, automated tests, code inspection?
		% \item How is the distribution of verification across developers?
		% \item Is there a dedicated team for QA?
	\end{itemize}

@@

	In order to perform the desired analyses, we needed access to the data recorded by Bugzilla for a specific project, including status changes and comments. We have found such data for two projects---Eclipse and NetBeans---from the domain of integrated development environments. The data was made available as part of the Mining Software Repositories 2011 Challenge\footnote{\url{http://2011.msrconf.org/msr-challenge.html}} in the form of MySQL database dumps. The files contain all data from the respective databases, except for developer profiles, omitted for privacy reasons.

@@

	Also, we have obtained the release dates for multiple versions of Eclipse and NetBeans. The information was obtained from the respective websites. In cases in which older information was not available, archived versions of the web pages were accessed via the website \url{www.archive.org}.

@@

	In Eclipse/Platform, the developer who fixes a bug often asks someone else to verify the fix, by asking ``please verify, [developer name]''. If the bug is reopened, then the fixer and the verifier exchange roles. This behavior illustrates a structured bug fixing/verification process.

@@

\small{This work is supported by FAPESB (grant BOL0119/2010) and CNPq/INES (grant 573964/2008-4).}
